---
title: "Analysis"
output: pdf_document
date: "2024-05-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source("Final/Functions.R")
source("Final/Functions_Plots.R")
```


```{r}
library(openxlsx)

root_folder = "Final/" 
subfolders = c("KM", "M500", "M100")
prefixes = c("A", "B", "C", "D")

for (subfolder in subfolders) {
  subfolder_path = file.path(root_folder, subfolder)
  
  for (prefix in prefixes) {
    folder_path = file.path(subfolder_path, prefix)
    
    files = list.files(path = folder_path, pattern = paste0("^", prefix, "_(KM|M500|M100)(_points)?.xlsx$"), full.names = TRUE)
    
    for (file in files) {
      file_name = tools::file_path_sans_ext(basename(file))
      
      assign(file_name, read.xlsx(file))
    }
  }
}
```


```{r}

for (subfolder in subfolders) {
  subfolder_path = file.path(root_folder, subfolder)
  
  for (prefix in prefixes) {
    folder_path = file.path(subfolder_path, prefix)
    
    # Load only files with "_dist_results" and "_points_results"
    dist_files = list.files(path = folder_path, pattern = paste0("^", prefix, "_(KM|M500|M100)_dist_result.xlsx$"), full.names = TRUE)
    points_files = list.files(path = folder_path, pattern = paste0("^", prefix, "_(KM|M500|M100)_points_result.xlsx$"), full.names = TRUE)
    
    # Read the distance result files
    for (file in dist_files) {
      file_name = tools::file_path_sans_ext(basename(file))
      assign(file_name, read.xlsx(file))
    }
    
    # Read the points result files
    for (file in points_files) {
      file_name = tools::file_path_sans_ext(basename(file))
      assign(file_name, read.xlsx(file))
    }
  }
}
```


# Analysis Technique for points

```{r, warning=FALSE, message=FALSE}
dataframes = list(Binary_KM = A_KM_points, Three_KM = B_KM_points, AW_KM = C_KM_points, ZINB_KM = D_KM_points, Binary_M500 = A_M500_points, Three_M500 = B_M500_points, AW_M500 = C_M500_points, ZINB_M500 = D_M500_points, Binary_M100 = A_M100_points, Three_M100 = B_M100_points, AW_M100 = C_M100_points, ZINB_M100 = D_M100_points)

comb_points = avg_avg_rmse(dataframes)
comb_points$method = c("Binary DM", "Three-class DM", "Areal Weighting", "ZINB", "Binary DM", "Three-class DM", "Areal Weighting", "ZINB", "Binary DM", "Three-class DM", "Areal Weighting", "ZINB")
comb_points <- comb_points %>%
  mutate(size = case_when(
    size == "km" ~ "kmxkm",
    size == "m500" ~ "500mx500m",
    size == "m100" ~ "100mx100m"
  ))

filt_comb_points <- comb_points %>%
  filter(!(method %in% c("Areal Weighting", "Three-class DM")))
```

```{r, warning=FALSE, message=FALSE}
generate_plot2(comb_points, c(0, 75000), "Average RMSE for Count variable per Method")
generate_plot2(filt_comb_points, c(0, 25000), "Average RMSE for Count variable per Method")
```


## KM

```{r, warning=FALSE, message=FALSE}
dataframes = list(A_KM_points = A_KM_points, B_KM_points = B_KM_points, C_KM_points = C_KM_points, D_KM_points = D_KM_points)
comb_km_points <- avg_rmse(dataframes)
```


```{r, message=FALSE}
subplot_titles <- c("Binary Mapping", "Three Class Mapping", "Areal Weighting", "Regression Mapping")

generate_plot(comb_km_points, c(0, 90000), "Average RMSE for Population Distribution per Mapping Technique, 1kmx1km")
```

```{r, message=FALSE}
filtered_results <- comb_km_points[comb_km_points$dataframe %in% c("A_KM_points", "B_KM_points", "D_KM_points"),]

generate_plot(filtered_results,c(5000, 30000), "Average RMSE for Population Distribution per Mapping Technique, 1kmx1km" )
```

## M500

```{r, message=FALSE}
dataframes = list(A_M500_points = A_M500_points, B_M500_points = B_M500_points, C_M500_points = C_M500_points, D_M500_points = D_M500_points)

comb_m500_points = avg_rmse(dataframes)
```



```{r, message=FALSE}
subplot_titles <- c("Binary Mapping", "Three Class Mapping", "Areal Weighting", "Regression Mapping")

generate_plot(comb_m500_points, c(0,90000), "Average RMSE for Population Distribution per Mapping Technique, 500mx500m")
```

```{r, message=FALSE}
filtered_results <- comb_m500_points[comb_m500_points$dataframe %in% c("A_M500_points", "B_M500_points"),]

generate_plot(filtered_results, c(5000, 30000), "Average RMSE for Population Distribution per Mapping Technique, 500mx500m")
```

## M100

```{r, message=FALSE}
dataframes = list(A_M100_points = A_M100_points, B_M100_points = B_M100_points, C_M100_points = C_M100_points, D_M100_points = D_M100_points)

comb_m100_points = avg_rmse(dataframes)

#print(comb_m100_points)
```

```{r, message=FALSE}
subplot_titles <- c("Binary Mapping", "Three Class Mapping", "Areal Weighting", "Regression Mapping")

generate_plot(comb_m100_points, c(0, 75000),"Average RMSE for Population Distribution per Mapping Technique, 100mx100m" )
```



```{r, message=FALSE}
filtered_results <- comb_m100_points[comb_m100_points$dataframe %in% c("A_M100_points", "B_M100_points"),]

generate_plot(filtered_results,c(5000, 30000), "Average RMSE for Population Distribution per Mapping Technique, 100mx100m")
```

# Analysis size for points

## Technique A

```{r, warning=FALSE, message=FALSE}
dataframes = list(A_KM_points = A_KM_points, A_M500_points = A_M500_points, A_M100_points = A_M100_points)
comb_a_points = avg_rmse(dataframes)

#print(comb_a_points)
```

```{r, message=FALSE}
subplot_titles <- c("1KMx1KM", "500Mx500M", "100Mx100M")

generate_plot(comb_a_points, c(0, 30000), "Average RMSE for Population Distribution per Size for Binary Mapping")
```

```{r}
tech_A = rbind(A_KM_points, A_M500_points, A_M100_points)
summary(aov(rmse ~ size, data = tech_A))
summary(aov(rmse ~ position, data = tech_A))
```

## Technique B (three-class)

```{r, warning=FALSE, message=FALSE}
dataframes = list(B_KM_points = B_KM_points, B_M500_points = B_M500_points, B_M100_points = B_M100_points)
comb_b_points = avg_rmse(dataframes)

print(comb_b_points)
```

```{r, message=FALSE}
subplot_titles <- c("1KMx1KM", "500Mx500M", "100Mx100M")

generate_plot(comb_b_points, c(0, 30000), "Average RMSE for Population Distribution  per Size for Three-Class Mapping")
```

```{r}
tech_B = rbind(B_KM_points, B_M500_points, B_M100_points)
summary(aov(rmse ~ size, data = tech_B))
summary(aov(rmse ~ position, data = tech_B))
summary(aov(rmse ~ size + position, data = tech_B))
```

## Technique C (areal)

```{r, warning=FALSE, message=FALSE}
dataframes = list(C_KM_points = C_KM_points, C_M500_points = C_M500_points, C_M100_points = C_M100_points)
comb_c_points = avg_rmse(dataframes)

#print(comb_b_points)
```

```{r, message=FALSE}
subplot_titles <- c("1KMx1KM", "500Mx500M", "100Mx100M")

generate_plot(comb_c_points, c(0, 90000), "Average RMSE for Population Distribution per size for Areal Weighting")
```


```{r}
tech_C = rbind(C_KM_points, C_M500_points, C_M100_points)
summary(aov(rmse ~ size, data = tech_C))
```

## Technique D (Regression)


```{r, warning=FALSE, message=FALSE}
dataframes = list(D_KM_points = D_KM_points, D_M500_points = D_M500_points, D_M100_points = D_M100_points)
comb_d_points = avg_rmse(dataframes)

#print(comb_b_points)
```

```{r, message=FALSE}
subplot_titles <- c("1KMx1KM", "500Mx500M", "100Mx100M")

generate_plot(comb_d_points, c(0, 30000), "Average RMSE for Population Distribution per size for Areal Weighting")
```


```{r}
tech_D = rbind(D_KM_points, D_M500_points, D_M100_points)
summary(aov(rmse ~ size, data = tech_D))
summary(aov(rmse ~ position + size, data = tech_D))
```

## Average RMSE

```{r}
# a: Binary Dasymetric Mapping - Count Variable
# b: Three-Class Dasymetric Mapping
# c: Areal Weighting
# d: ZINB
# km x km
mean(A_KM_points$rmse)
mean(B_KM_points$rmse)
mean(C_KM_points$rmse)
mean(D_KM_points$rmse)
```

```{r}
# 500m x 500m
mean(A_M500_points$rmse)
mean(B_M500_points$rmse)
mean(C_M500_points$rmse)
mean(D_M500_points$rmse)
```

```{r}
# 500m x 500m
mean(A_M100_points$rmse)
mean(B_M100_points$rmse)
mean(C_M100_points$rmse)
mean(D_M100_points$rmse)
```


# Coefficient of Variation

```{r}
# Binary Dasymetric Mapping
cv_a_km = calculate_cv(A_KM_points_result)
cv_a_m500 = calculate_cv(A_M500_points_result)
cv_a_m100 = calculate_cv(A_M100_points_result)

cv_plot(cv_a_km, ylimit = c(0,25), title = "km x km")
cv_plot(cv_a_m500, ylimit = c(0,25), title = "500m x 500m")
cv_plot(cv_a_m100, ylimit = c(0,25), title = "100m x 100m")
```



```{r}
# Three-Class Dasymetric Mapping
cv_b_km = calculate_cv(B_KM_points_result)
cv_b_m500 = calculate_cv(B_M500_points_result)
cv_b_m100 = calculate_cv(B_M100_points_result)

cv_plot(cv_b_km, ylimit = c(0,25), title = "km x km")
cv_plot(cv_b_m500, ylimit = c(0,25), title = "500m x 500m")
cv_plot(cv_b_m100, ylimit = c(0,25), title = "100m x 100m")
```

```{r}
# Areal Weighting
cv_c_km = calculate_cv(C_KM_points_result)
cv_c_m500 = calculate_cv(C_M500_points_result)
cv_c_m100 = calculate_cv(C_M100_points_result)

cv_plot(cv_c_km, ylimit = c(0,25), title = "km x km")
cv_plot(cv_c_m500, ylimit = c(0,25), title = "500m x 500m")
cv_plot(cv_c_m100, ylimit = c(0,25), title = "100m x 100m")
```

```{r}
# ZINB

cv_d_km = calculate_cv(D_KM_points_result)
cv_d_m500 = calculate_cv(D_M500_points_result)
cv_d_m100 = calculate_cv(D_M100_points_result)

cv_plot(cv_d_km, ylimit = c(0,75), title = "km x km")
cv_plot(cv_d_m500, ylimit = c(0,75), title = "500m x 500m")
cv_plot(cv_d_m100, ylimit = c(0,75), title = "100m x 100m")
```

```{r}
sum(cv_d_km$cv > 30)
```

```{r}
# a: Binary Dasymetric Mapping - Count Variable
# b: Three-Class Dasymetric Mapping
# c: Areal Weighting
# d: ZINB
# km x km
mean(cv_a_km$cv)
mean(cv_b_km$cv)
mean(cv_c_km$cv)
mean(cv_d_km$cv)
```

```{r}
# 500m x 500m 
mean(cv_a_m500$cv)
mean(cv_b_m500$cv)
mean(cv_c_m500$cv)
mean(cv_d_m500$cv)
```

```{r}
# 100m x 100m
mean(cv_a_m100$cv)
mean(cv_b_m100$cv)
mean(cv_c_m100$cv)
mean(cv_d_m100$cv)
```

## ANOVA tests

```{r}
A_rmse_points = rbind(A_KM_points, A_M500_points, A_M100_points)
B_rmse_points = rbind(B_KM_points, B_M500_points, B_M100_points)
C_rmse_points = rbind(C_KM_points, C_M500_points, C_M100_points)
D_rmse_points = rbind(D_KM_points, D_M500_points, D_M100_points)
```

```{r}
# binary
anova_result = aov(rmse ~ size + position, data = A_rmse_points)
summary(anova_result)
```

```{r}
anova_result = aov(rmse ~ size + position, data = B_rmse_points)
summary(anova_result)
```

```{r}
anova_result = aov(rmse ~ size + position, data = C_rmse_points)
summary(anova_result)
```

```{r}
# zinb
anova_result = aov(rmse ~ size + position, data = D_rmse_points)
summary(anova_result)
```

### Estimations

```{r}
A_est_points = rbind(A_KM_points_result, A_M500_points_result, A_M100_points_result)
B_est_points = rbind(B_KM_points_result, B_M500_points_result, B_M100_points_result)
C_est_points = rbind(C_KM_points_result, C_M500_points_result, C_M100_points_result)
D_est_points = rbind(D_KM_points_result, D_M500_points_result, D_M100_points_result)
```

```{r}
A_est_points$standardized_est <- ave(A_est_points$sum_value, A_est_points$GM_NAAM, FUN = scale)
anova_result_standardized <- aov(standardized_est ~ size + position, data = A_est_points)
summary(anova_result_standardized)
```

```{r}
B_est_points$standardized_est <- ave(B_est_points$sum_value, B_est_points$GM_NAAM, FUN = scale)
anova_result_standardized <- aov(standardized_est ~ size + position, data = B_est_points)
summary(anova_result_standardized)
```

```{r}
C_est_points$standardized_est <- ave(C_est_points$sum_value, C_est_points$GM_NAAM, FUN = scale)
anova_result_standardized <- aov(standardized_est ~ size + position, data = C_est_points)
summary(anova_result_standardized)
```

```{r}
D_est_points$standardized_est <- ave(D_est_points$sum_value, D_est_points$GM_NAAM, FUN = scale)
anova_result_standardized <- aov(standardized_est ~ size + position, data = D_est_points)
summary(anova_result_standardized)
```



# Analysis Technique for Distance Variable

```{r, warning=FALSE, message=FALSE, warning = False}
dataframes = list(Binary_KM = A_KM, Three_KM = B_KM, AW_KM = C_KM, ZINB_KM = D_KM, Binary_M500 = A_M500, Three_M500 = B_M500, AW_M500 = C_M500, ZINB_M500 = D_M500, Binary_M100 = A_M100, Three_M100 = B_M100, AW_M100 = C_M100, ZINB_M100 = D_M100 )

comb  = avg_avg_rmse(dataframes)
comb $method = c("Binary DM", "Three-class DM", "Areal Weighting", "ZINB", "Binary DM", "Three-class DM", "Areal Weighting", "ZINB", "Binary DM", "Three-class DM", "Areal Weighting", "ZINB")
comb  <- comb  %>%
  mutate(size = case_when(
    size == "km" ~ "kmxkm",
    size == "m500" ~ "500mx500m",
    size == "m100" ~ "100mx100m"
  ))

filt_comb  <- comb  %>%
  filter(!(method %in% c("Areal Weighting", "Three-class DM")))
```

```{r, warning=FALSE, message=FALSE}
generate_plot2(comb, c(0, 200), "Average RMSE for Count variable per Method")
generate_plot2(filt_comb, c(0, 200), "Average RMSE for Count variable per Method")
```

## km

```{r, warning=FALSE, message=FALSE}
dataframes = list(A_KM = A_KM, B_KM = B_KM, C_KM = C_KM, D_KM = D_KM)
comb_km <- avg_rmse(dataframes)
#print(comb_km)
```

```{r, message=FALSE}
subplot_titles <- c("Binary Mapping", "Three Class Mapping", "Areal Weighting", "Regression Mapping")

generate_plot(comb_km, c(0, 250), "Average RMSE for Distance variable per Mapping Technique, 1kmx1km")
```

```{r, message=FALSE}
filtered_results <- comb_km[comb_km$dataframe %in% c("A_KM", "B_KM"),]

generate_plot(filtered_results,c(0, 100),"Average RMSE for Distance variable per Mapping Technique, 1kmx1km" )
```

## M500

```{r, message=FALSE}
dataframes = list(A_M500 = A_M500, B_M500 = B_M500, C_M500 = C_M500, D_M500 = D_M500)

comb_m500 = avg_rmse(dataframes)

#print(comb_m500)
```


```{r, message=FALSE}
subplot_titles <- c("Binary Mapping", "Three Class Mapping", "Areal Weighting", "Regression Mapping")

generate_plot(comb_m500, c(0, 250), "Average RMSE for Distance variable per Mapping Technique, 500mx500m")
```

```{r, message=FALSE}
filtered_results <- comb_m500[comb_m500$dataframe %in% c("A_M500", "B_M500"),]

generate_plot(filtered_results, c(0, 100),  "Average RMSE for Distance variable per Mapping Technique, 500mx500m")
```

## M100


```{r, message=FALSE}
dataframes = list(A_M100 = A_M100, B_M100 = B_M100, C_M100 = C_M100, D_M100 = D_M100)

comb_m100 = avg_rmse(dataframes)

print(comb_m100)
```

```{r, message=FALSE}
subplot_titles <- c("Binary Mapping", "Three Class Mapping", "Areal Weighting", "Regression Mapping")

generate_plot(comb_m100, c(0, 250),"Average RMSE for Distance variable per Mapping Technique, 100mx100m" )
```


# Analysis size for distance variable
## Technique A (binary)

```{r, warning=FALSE, message=FALSE}
dataframes = list(A_KM = A_KM, A_M500 = A_M500, A_M100 = A_M100)
comb_a = avg_rmse(dataframes)

#print(comb_a)
```

```{r, message=FALSE}
subplot_titles <- c("1KMx1KM", "500Mx500M", "100Mx100M")

generate_plot(comb_a, c(0, 100), "Average RMSE for Distance Variable  per Size for Binary Mapping")
```

```{r}
A = rbind(A_KM, A_M500, A_M100)
summary(aov(rmse ~ size + position, data = A))
```

## Technique B (three-class)

```{r, warning=FALSE, message=FALSE}
dataframes = list(B_KM = B_KM, B_M500 = B_M500, B_M100 = B_M100)
comb_b = avg_rmse(dataframes)

#print(comb_b)
```

```{r, message=FALSE}
subplot_titles <- c("1KMx1KM", "500Mx500M", "100Mx100M")

generate_plot(comb_b, c(0, 100), "Average RMSE for Distance Variable per Size for Three-Class Mapping")
```

```{r}
B = rbind(B_KM, B_M500, B_M100)
summary(aov(rmse ~ size + position, data = B))
```

## Technique C (areal)
```{r, warning=FALSE, message=FALSE}
dataframes = list(C_KM = C_KM, C_M500 = C_M500, C_M100 = C_M100)
comb_c = avg_rmse(dataframes)

#print(comb_c)
```

```{r, message=FALSE}
subplot_titles = c("1KMx1KM", "500Mx500M", "100Mx100M")

generate_plot(comb_c, c(0, 250), "Average RMSE for Population Distribution per size for Areal Weighting")
```

```{r}
C = rbind(C_KM, C_M500, C_M100)
summary(aov(rmse ~ size, data = C))
```

## Technique D (Regression)

```{r, warning=FALSE, message=FALSE}
dataframes = list(D_KM = D_KM, D_M500 = D_M500, D_M100 = D_M100)
comb_d = avg_rmse(dataframes)

#print(comb_d)
```

```{r, message=FALSE}
subplot_titles <- c("1KMx1KM", "500Mx500M", "100Mx100M")

generate_plot(comb_d, c(0, 150), "Average RMSE for Distance Variable  per Size for Binary Mapping")
```

```{r}
D = rbind(D_KM, D_M500, D_M100)
summary(aov(rmse ~ size, data = D))
```

## Average RMSE

```{r}
# a: Binary Dasymetric Mapping - Count Variable
# b: Three-Class Dasymetric Mapping
# c: Areal Weighting
# d: ZINB
# km x km
mean(A_KM$rmse)
mean(B_KM$rmse)
mean(C_KM$rmse)
mean(D_KM$rmse)
```

```{r}
# 500m x 500m
mean(A_M500$rmse)
mean(B_M500$rmse)
mean(C_M500$rmse)
mean(D_M500$rmse)
```
```{r}
# 100m x 100m
mean(A_M100$rmse)
mean(B_M100$rmse)
mean(C_M100$rmse)
mean(D_M100$rmse)
```

# Coefficient of Variation


```{r}
# Binary Dasymetric Mapping
cv_a_km_dist = calculate_cv2(A_KM_dist_result)
cv_a_m500_dist = calculate_cv2(A_M500_dist_result)
cv_a_m100_dist = calculate_cv2(A_M100_dist_result)

cv_plot(cv_a_km_dist, ylimit = c(0,25), title = "km x km")
cv_plot(cv_a_m500_dist, ylimit = c(0,25), title = "500m x 500m")
cv_plot(cv_a_m100_dist, ylimit = c(0,25), title = "100m x 100m")
```

```{r}
#Three-Class Dasymetric Mapping
cv_b_km_dist = calculate_cv2(B_KM_dist_result)
cv_b_m500_dist = calculate_cv2(B_M500_dist_result)
cv_b_m100_dist = calculate_cv2(B_M100_dist_result)

cv_plot(cv_b_km_dist, ylimit = c(0,25), title = "km x km")
cv_plot(cv_b_m500_dist, ylimit = c(0,25), title = "500m x 500m")
cv_plot(cv_b_m100_dist, ylimit = c(0,25), title = "100m x 100m")
```

```{r}
# Areal Weighting
cv_c_km_dist = calculate_cv2(C_KM_dist_result)
cv_c_m500_dist = calculate_cv2(C_M500_dist_result)
cv_c_m100_dist = calculate_cv2(C_M100_dist_result)

cv_plot(cv_c_km_dist, ylimit = c(0,25), title = "km x km")
cv_plot(cv_c_m500_dist, ylimit = c(0,25), title = "500m x 500m")
cv_plot(cv_c_m100_dist, ylimit = c(0,25), title = "100m x 100m")
```

```{r}
cv_d_km_dist = calculate_cv2(D_KM_dist_result)
cv_d_m500_dist = calculate_cv2(D_M500_dist_result)
cv_d_m100_dist = calculate_cv2(D_M100_dist_result)

cv_plot(cv_d_km_dist, ylimit = c(0,25), title = "km x km")
cv_plot(cv_d_m500_dist, ylimit = c(0,25), title = "500m x 500m")
cv_plot(cv_d_m100_dist, ylimit = c(0,25), title = "100m x 100m")
```

```{r}
# a: Binary Dasymetric Mapping - Count Variable
# b: Three-Class Dasymetric Mapping
# c: Areal Weighting
# d: ZINB
# km x km
mean(cv_a_km_dist$cv)
mean(cv_b_km_dist$cv)
mean(cv_c_km_dist$cv)
mean(cv_d_km_dist$cv)
```

```{r}
# 500m x 500m
mean(cv_a_m500_dist$cv)
mean(cv_b_m500_dist$cv)
mean(cv_c_m500_dist$cv)
mean(cv_d_m500_dist$cv)
```


```{r}
# 100m x 100m
mean(cv_a_m100_dist$cv)
mean(cv_b_m100_dist$cv)
mean(cv_c_m100_dist$cv)
mean(cv_d_m100_dist$cv)
```

## ANOVA tests

### RMSE

```{r}
A_rmse_dist = rbind(A_KM, A_M500, A_M100)
B_rmse_dist = rbind(B_KM, B_M500, B_M100)
C_rmse_dist = rbind(C_KM, C_M500, C_M100)
D_rmse_dist = rbind(D_KM, D_M500, D_M100)
```

```{r}
# binary
anova_result = aov(rmse ~ size + position, data = A_rmse_dist)
summary(anova_result)
```

```{r}
anova_result = aov(rmse ~ size + position, data = B_rmse_dist)
summary(anova_result)
```

```{r}
anova_result = aov(rmse ~ size + position, data = C_rmse_dist)
summary(anova_result)
```

```{r}
anova_result = aov(rmse ~ size + position, data = D_rmse_dist)
summary(anova_result)
```


### Estimations

```{r}
A_est_dist = rbind(A_KM_dist_result, A_M500_dist_result, A_M100_dist_result)
B_est_dist = rbind(B_KM_dist_result, B_M500_dist_result, B_M100_dist_result)
C_est_dist = rbind(C_KM_dist_result, C_M500_dist_result, C_M100_dist_result)
D_est_dist = rbind(D_KM_dist_result, D_M500_dist_result, D_M100_dist_result)
```

```{r}
A_est_dist$standardized_est <- ave(A_est_dist$ratio, A_est_dist$GM_NAAM, FUN = scale)

anova_result_standardized <- aov(standardized_est ~ size + position, data = A_est_dist)
summary(anova_result_standardized)
```


```{r}
B_est_dist$standardized_est <- ave(B_est_dist$ratio, B_est_dist$GM_NAAM, FUN = scale)

anova_result_standardized <- aov(standardized_est ~ size + position, data = B_est_dist)
summary(anova_result_standardized)
```

```{r}
C_est_dist$standardized_est <- ave(C_est_dist$ratio, C_est_dist$GM_NAAM, FUN = scale)

anova_result_standardized <- aov(standardized_est ~ size + position, data = C_est_dist)
summary(anova_result_standardized)
```

```{r}
D_est_dist$standardized_est <- ave(D_est_dist$ratio, D_est_dist$GM_NAAM, FUN = scale)

anova_result_standardized <- aov(standardized_est ~ size + position, data = D_est_dist)
summary(anova_result_standardized)
```



# Visualizations

```{r, message=FALSE, warning=FALSE}
library(sf)
nl_municipalities = st_read("/KM/gemeente.gpkg")
```


```{r}
sp_a_km_points = nl_municipalities %>%
  left_join(calc_summary(A_KM_points), by = "GM_NAAM")
sp_a_m100_points = nl_municipalities %>%
  left_join(calc_summary(A_M100_points), by = "GM_NAAM")
sp_d_m100_points = nl_municipalities %>%
  left_join(calc_summary(D_M100_points), by = "GM_NAAM")
```

```{r}
map_plot_me_points(sp_a_km_points, top_values = TRUE, x_offset = 0, y_offset = 7500, title = "Population Overestimated using Binary Dasymetric Mapping, 1kmx1km")
map_plot_me_points(sp_a_km_points, top_values = FALSE, x_offset = -18500, y_offset = 7500, title = "Population underestimated using Binary Dasymetric Mapping, 1kmx1km")
```


```{r}
map_plot_me_points(sp_a_m100_points, top_values = TRUE, x_offset = 0, y_offset = 8000, title = "Population Overestimated using Binary Dasymetric Mapping, 100mx100m")
map_plot_me_points(sp_a_m100_points, top_values = FALSE, x_offset = -19500, y_offset = -9500, title = "Population underestimated using Binary Dasymetric Mapping, 100mx100m")
```

```{r}
map_plot_me_points(sp_d_m100_points, top_values = TRUE, x_offset = -15000, y_offset = -500, title = "Population Overestimated using Regression Mapping, 100mx100m")
map_plot_me_points(sp_d_m100_points, top_values = FALSE, x_offset = -19500, y_offset = 8500, title = "Population underestimated using Regression Mapping, 100mx100m")
```


```{r}
map_plot_cv(sp_a_km_points, top_values = TRUE, x_offset = -12000, y_offset = -7500, title = "Coefficient Variation per Municipality using Binary Dasymetric Mapping, 1kmx1km")
map_plot_cv(sp_a_km_points, top_values = FALSE, x_offset = -12000, y_offset = -7500, title = "Coefficient Variation per Municipality using Binary Dasymetric Mapping, 1kmx1km")
map_plot_se(sp_a_km_points, top_values = TRUE, x_offset = -12000, y_offset = 12500, title = "Standard Deviation per Municipality using Binary Dasymetric Mapping, 1kmx1km")
```


```{r}
sp_a_km = nl_municipalities %>%
  left_join(calc_summary(A_KM), by = "GM_NAAM")
sp_a_m100 = nl_municipalities %>%
  left_join(calc_summary(A_M100), by = "GM_NAAM")
sp_b_m100 = nl_municipalities %>%
  left_join(calc_summary(B_M100), by = "GM_NAAM")
sp_d_m100 = nl_municipalities %>%
  left_join(calc_summary(D_M100), by = "GM_NAAM")
```


```{r}
map_plot_me(sp_a_m100, top_values = TRUE, x_offset = -10000, y_offset = 7500, title = "Distance Variable Overestimated using Binary Dasymetric Mapping, 100mx100m")
map_plot_me(sp_a_m100, top_values = FALSE, x_offset = 10000, y_offset = 7500, title = "Distance Variable underestimated using Binary Dasymetric Mapping, 100mx100m")
```

```{r}
map_plot_me(sp_b_m100, top_values = TRUE, x_offset = -5000, y_offset = 10000, title = "Distance Variable Overestimated using Three-Class Dasymetric Mapping, 100mx100m")
map_plot_me(sp_b_m100, top_values = FALSE, x_offset = 5000, y_offset = 10000, title = "Distance Variable underestimated using Three-Class Dasymetric Mapping, 100mx100m")
```


```{r}
map_plot_me(sp_d_m100, top_values = TRUE, x_offset = -7500, y_offset = 7500, title = "Distance Variable Overestimated using Regression Mapping, 100mx100m")
map_plot_me(sp_d_m100, top_values = FALSE, x_offset = 10000, y_offset = 7500, title = "Distance Variable underestimated using Regression Mapping, 100mx100m")
```


```{r}
map_plot_cv(sp_a_km, top_values = TRUE, x_offset = 25500, y_offset = 23500, title = "Coefficient Variation per Municipality using Binary Dasymetric Mapping, 1kmx1km")
map_plot_se(sp_a_km, top_values = TRUE, x_offset = 2000, y_offset = -8500, title = "Standard Deviation per Municipality using Binary Dasymetric Mapping, 1kmx1km")
```


```{r}
ggplot(data = sp_a_m100) +
  geom_sf(aes(fill = avg_me)) +
  scale_fill_gradient(low = "lightblue", high = "darkblue", name = "Average Error") +
  labs(title = "Average Error Distance for Binary Mapping, 100mx100m") +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank())

ggplot(data = sp_d_m100) +
  geom_sf(aes(fill = avg_me)) +
  scale_fill_gradient(low = "lightblue", high = "darkblue", name = "Average Error") +
  labs(title = "Average Error Distance for Regression Mapping, 100mx100m") +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank())
```

```{r}
ggplot(data = sp_a_m100_points) +
  geom_sf(aes(fill = avg_me)) +
  scale_fill_gradient(low = "lightblue", high = "darkblue", name = "Average Error") +
  labs(title = "Average Error Population for Binary Mapping 100mx100m") +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank())

ggplot(data = sp_d_m100_points) +
  geom_sf(aes(fill = avg_me)) +
  scale_fill_gradient(low = "lightblue", high = "darkblue", name = "Average Error") +
  labs(title = "Average Error Population for Regression Mapping, 100mx100m") +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank())
```




